\documentclass[11pt,reqno]{amsart}

\usepackage{amsmath,amssymb,amsthm}
\usepackage[margin=1.1in]{geometry}
\usepackage{microtype}
\usepackage{tikz}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}

\theoremstyle{plain}
\newtheorem{theorem}{Theorem}[section]
\newtheorem{proposition}[theorem]{Proposition}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
\newtheorem{remark}[theorem]{Remark}
\newtheorem{example}[theorem]{Example}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{computation}[theorem]{Computation}

\newcommand{\R}{\mathbb{R}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\F}{\mathbb{F}}
\newcommand{\HH}{\mathbb{H}}
\newcommand{\SU}{\mathrm{SU}(2)}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\Inat}{I^{\natural}}
\newcommand{\HF}{\mathit{HF}}
\newcommand{\CF}{\mathit{CF}}
\newcommand{\Kh}{\mathit{Kh}}
\newcommand{\gr}{\operatorname{gr}}
\newcommand{\rk}{\operatorname{rank}}
\newcommand{\sgn}{\operatorname{sgn}}
\newcommand{\Sig}{\Sigma}
\newcommand{\pill}{P}
\newcommand{\Rnat}{\mathcal{R}^{\natural}}
\newcommand{\Rp}{\mathcal{R}}
\newcommand{\iss}{\looparrowright}
\newcommand{\bc}{b}
\newcommand{\Qh}[1]{\widehat{Q_{#1}}}

\begin{document}

\title[Instanton homology of $(-2,3,q)$ pretzels and pillowcase cochains]
{The instanton homology of the $(-2,3,q)$ pretzel knots\\ and computed bounding cochains in the pillowcase}

\author{Bernd J. Wuebben}
\subjclass[2020]{57R58 (primary); 57K10, 57K18, 57K31, 53D40 (secondary)}
\keywords{Singular instanton homology, pretzel knots, pillowcase,
Lagrangian Floer homology, bounding cochains, Atiyah--Floer conjecture,
Khovanov homology}
\date{July 17, 2026}

\begin{abstract}
We prove that the reduced singular instanton knot homology of the pretzel knots $P(-2,3,q)$ has rank
$q+2$ for every odd $q\ge3$: the Alexander polynomials of the family, computed in closed form by a
skein recursion (they are Hironaka's Lehmer-like polynomials, with all coefficients in $\{0,\pm1\}$),
give the lower bound $q+2$, and Manion's closed-form reduced Khovanov homology gives the matching upper
bound. We then compare this against the pillowcase (symplectic) side of the knot Atiyah--Floer program.
Working in the immersed-curve combinatorial model of Herald--Kirk and Smith, we reconstruct the
pillowcase Lagrangians of the natural tangle decomposition of the family and compute the naive
Lagrangian--Floer homology of its members through $q=13$. The outcome is a sharp experimental law: the
naive rank differs from $\rk\Inat$ by \emph{exactly one differential},
\[
   \text{naive rank} \;-\; \rk\Inat \;=\; 2\,\sgn(\det K - 3),
\]
vanishing for the torus member $q=3$ and changing direction as the determinant $\det=|q-6|$ crosses $3$
(equivalently, as binary-dihedral traceless characters appear). Finally we compute the bounding
cochains --- the correction terms conjectured by Cazassus--Herald--Kirk--Kotelskiy --- that repair the
deficiency: for $q=5$ a unique two-crossing cochain acting through an immersed quadrilateral, for $q=7$
a unique single crossing acting through a triangle (each \emph{cancelling} a bigon and raising the rank
by $2$), and for $q=11$ single-crossing cochains acting in the \emph{opposite} direction (creating a
differential and lowering the rank by $2$). These are, to our knowledge, the first explicitly computed
nonzero bounding cochains in pillowcase Floer theory, and they realize both directions of the
conjectured correction within a single family, with a marked rigidity asymmetry: cancellation admits a
unique minimal cochain, creation many. We separate throughout what is proved unconditionally, what is
computed within the combinatorial model, and what remains conjectural.
\end{abstract}

\maketitle

\section{Introduction}\label{sec:intro}

\subsection{Two homologies for one knot}
Let $K\subset S^3$ be a knot. On the gauge-theoretic side sits the reduced singular instanton knot
homology $\Inat(K)$ of Kronheimer--Mrowka \cite{KM1,KM2}, whose graded Euler characteristic is the
Alexander polynomial \cite{Lim,KM1} and which receives a spectral sequence from reduced Khovanov
homology \cite{KM2}; hence
\begin{equation}\label{eq:squeeze}
   \ell(K):=\textstyle\sum_i |a_i(\Delta_K)| \;\le\; \rk \Inat(K) \;\le\; \dim \Kh_r(K)=:u(K).
\end{equation}
On the symplectic side sits the pillowcase program of Hedden--Herald--Kirk \cite{HHK1,HHK2}. Present
$K=(B^3,T_1)\cup_{(S^2,4)}(B^3,T_2)$ as a union of two tangles. The traceless $\SU$ character variety
of the four-punctured sphere is the \emph{pillowcase}
\[
   \pill=(\R/2\pi\Z)^2/\iota,\qquad \iota(\gamma,\theta)=(-\gamma,-\theta),
\]
a two-sphere with four $\Z/2$ orbifold points and symplectic form $d\gamma\wedge d\theta$ on the smooth
locus $\pill^*$ \cite{Lin,HHK1}. Each tangle determines an immersed Lagrangian
$\Rp_{\pi_i}(T_i)\iss\pill^*$, the intersections $\Rp_{\pi_1}(T_1)\cap\Rp_{\pi_2}(T_2)$ are the
traceless representations of the knot group, and one forms their Lagrangian--Floer homology --- an
intended Atiyah--Floer counterpart of $\Inat(K)$.

This naive Floer homology is \emph{not} a knot invariant: figure-eight bubbling at the curves'
self-intersections spoils invariance under tangle moves. Cazassus, Herald, Kirk and Kotelskiy
\cite{CHKK} conjectured the repair: each tangle carries a \emph{bounding cochain}
$\bc\in\CF(\Rp(T),\Rp(T))$, an $\F_2$-combination of the self-intersection points satisfying the
Maurer--Cartan equation
\begin{equation}\label{eq:MC}
   \sum_{k\ge0}\mu^k(\bc,\dots,\bc)=0
\end{equation}
($\mu^k$ counts immersed $(k{+}1)$-gons), and the $\bc$-deformed Floer homology
$\HF\big((\Rp(T_1),\bc_1),(\Rp(T_2),\bc_2)\big)$ is conjecturally the knot invariant, equal to
$\Inat(K)$ \cite[Conj.~1.1]{CHKK}. Before this work, one bounding cochain had been exhibited (on the
earring tangle of $T(4,5)$ \cite[\S10]{CHKK}), one had been proven nonzero without being computed (the
Conway-sum tangle of $P(-2,3,5)$, Smith \cite[Thm.~5.9]{Smith}), and none had been computed.

This paper studies both sides for the pretzel family
\begin{equation}\label{eq:family}
   K_q := P(-2,3,q)=\operatorname{num}\big(Q_{-1/2}+Q_{1/3}+Q_{1/q}\big),
   \qquad q\ge3 \text{ odd},
\end{equation}
whose smallest members are the torus knots $K_3=T(3,4)=8_{19}$ and $K_5=T(3,5)=10_{124}$, and which
contains the celebrated $K_7=P(-2,3,7)$. We prove an unconditional theorem on the instanton side,
measure the pillowcase side against it, and compute the correcting cochains.

\subsection{The instanton side: a theorem}
\begin{theorem}\label{thm:inat}
For every odd $q\ge3$,
\[
   \rk\Inat(P(-2,3,q)) \;=\; q+2 .
\]
\end{theorem}

The proof occupies Section~\ref{sec:inat} and is an assembly of three ingredients, of which only the
first requires computation. (i) The Alexander polynomials of the family are, up to units and the
substitution $t\mapsto-t$, the Lehmer-like polynomials
\begin{equation}\label{eq:alex}
   \Delta_{K_q}(t)\;\doteq\;
   t^{g}+t^{g-1}\;-\!\!\sum_{j=-(g-3)}^{g-3}\!\! t^{j}\;+\;t^{-(g-1)}+t^{-g},
   \qquad g=\tfrac{q+3}2,
\end{equation}
with all coefficients in $\{0,\pm1\}$: two ones at each end, one internal zero on each side, and a
solid block of $q-2$ signed ones in the middle, so $\ell(K_q)=4+(q-2)=q+2$. We derive
\eqref{eq:alex} from the Conway skein relation applied in the $q$-twist band, which produces a
three-term Chebyshev-type recursion solvable in closed form; the polynomials agree with Hironaka's
family \cite{Hironaka} (for $q=7$, \eqref{eq:alex} is precisely Lehmer's polynomial). (ii) Manion's
closed-form computation of the reduced Khovanov homology of non-quasi-alternating $3$-strand pretzels
\cite[Thm.~1.1]{Manion} gives, for $P(-2,3,q)$, $\dim\Kh_r=2^2+(3-2)(q-2)=q+2$. (iii) The squeeze
\eqref{eq:squeeze} closes the gap. To our knowledge Theorem~\ref{thm:inat} has not appeared in the
literature (the case $q=5$ is Smith's \cite{Smith}); it is elementary given \cite{Manion,Hironaka},
but it is exactly the input the pillowcase comparison needs, and it is unconditional --- no immersed-curve
model and no conjecture enters.

\subsection{The pillowcase side: a deficiency law}
For the decomposition \eqref{eq:family} take $T_1=\Qh{-1/2}$ (with the earring added, so its bounding
cochain vanishes \cite[Lem.~5.6]{Smith}) and $T_2=Q_{1/3}+Q_{1/q}$, with $\gcd(q,3)=1$ so that the
Conway sum is corner-circle free. We reconstructed the two Lagrangians from the quaternionic
representation theory --- validating the reconstruction against every number in \cite{Smith} for $q=5$
(Section~\ref{ss:gate}) --- and computed the \emph{naive} ($\bc=0$) Lagrangian--Floer homology of the
pair for the family members through $q=13$, at two independent perturbations each. The result
(Table~\ref{tab:family}):

\begin{computation}[Deficiency law]\label{comp:law}
For $q\in\{3,5,7,11,13\}$, at every tested perturbation,
\[
   \rk\HF\big((\Rnat(T_1),0),(\Rp_t(T_2),0)\big)\;-\;\rk\Inat(K_q)
   \;=\; 2\,\sgn\!\big(\det K_q-3\big),
   \qquad \det K_q=|q-6|.
\]
That is: the naive pillowcase homology is \emph{exact} for the torus member $q=3$; it is \emph{too
small by one differential} for $q=5,7$ ($\det=1$); and it is \emph{too large by one differential} for
$q=11,13$ ($\det\ge5$).
\end{computation}

\begin{table}[ht]
\centering
\small
\begin{tabular}{c|cccccc}
 $q$ & knot & $\det$ & naive $\rk\HF$ & $\rk\Inat$ & naive $-\Inat$ & correction \\ \hline
 $3$ & $8_{19}=T(3,4)$ & $3$ & $5$ & $5$ & $0$ & none ($\bc=0$) \\
 $5$ & $10_{124}=T(3,5)$ & $1$ & $5$ & $7$ & $-2$ & cancel a bigon \\
 $7$ & $P(-2,3,7)$ & $1$ & $7$ & $9$ & $-2$ & cancel a bigon \\
 $11$ & $P(-2,3,11)$ & $5$ & $15$ & $13$ & $+2$ & create a differential \\
 $13$ & $P(-2,3,13)$ & $7$ & $17$ & $15$ & $+2$ & (predicted) \\
\end{tabular}
\medskip
\caption{The family \eqref{eq:family}. Naive ranks are computed in the combinatorial model at two
independent perturbations each (identical values). $\rk\Inat=q+2$ is Theorem~\ref{thm:inat},
unconditional. The deficiency is $\pm2$ or $0$ --- always exactly one differential --- with the sign
governed by $\det\gtrless3$; equivalently by the number $d=(\det-1)/2$ of binary-dihedral traceless
characters ($d=0$: deficit; $d=1$: exact; $d\ge2$: excess).}
\label{tab:family}
\end{table}

We emphasize the register: the naive ranks are computed within the immersed-curve combinatorial model
(as is every computation in this subject); the law of Computation~\ref{comp:law} is verified at five
members and two perturbations each, and is a conjecture beyond them. What makes it sharp is
Theorem~\ref{thm:inat}: without the unconditional value of $\rk\Inat$ the deficiency could not be
measured at all. Note also what the law killed: the naive rank is \emph{not} monotone in any obvious
knot complexity (it is $5,5,7,15,17$), and simpler candidate laws (e.g.\ deficiency proportional to
$\det-3$) are refuted by $q=13$.

\subsection{The bounding cochains: both directions realized}
The conjectural repair must therefore \emph{add} rank $2$ for $q=5,7$ and \emph{remove} rank $2$ for
$q\ge11$. Over $\F_2$, adding rank $2$ to the homology means \emph{cancelling} one differential
(the deformation removes a bigon from the differential), and removing rank $2$ means \emph{creating}
one. We compute cochains doing both.

\begin{computation}[The cochains]\label{comp:cochains}
Within the combinatorial model, with $\bc$ supported on the self-intersections of
$\mathrm{blue}=\Rp_t(Q_{1/3}+Q_{1/q})$:
\begin{enumerate}
\item[(i)] \emph{($q=5$; deficit.)} The unique minimal bounding cochain with deformed rank
$7=\rk\Inat$ is $\bc=s_A+s_B$, two self-intersections at
$(\gamma,\theta)\approx(0.03,1.27)$ and $(3.06,4.98)$, one on each pillowcase seam; it acts through a
single immersed \emph{quadrilateral} ($\mu^3$) that cancels one of the two bigons.
\item[(ii)] \emph{($q=7$; deficit.)} The unique minimal bounding cochain with deformed rank
$9=\rk\Inat$ is a \emph{single} self-intersection at $\approx(0.05,5.41)$; it acts through an immersed
\emph{triangle} ($\mu^2$) that cancels one of the three bigons.
\item[(iii)] \emph{($q=11$; excess.)} There are \emph{fifty-five} single-crossing Maurer--Cartan-valid
bounding cochains with deformed rank $13=\rk\Inat$; each acts through an immersed triangle that
\emph{creates} one new differential, and all but a handful of the created differentials flow into one
distinguished generator.
\end{enumerate}
All values are stable under change of the perturbation parameters, and each cochain satisfies the
Maurer--Cartan equation \eqref{eq:MC} to the computed orders (for $q=5$ the equation is vacuous on
small support; for $q=7,11$ the self-differential $\mu^1$ is nonzero and the support crossings are
$\mu^1$-closed).
\end{computation}

These are the first explicitly computed nonzero bounding cochains in pillowcase Floer theory, and
items (i)/(ii) versus (iii) realize the two directions of the conjectured correction within one
family. Two structural contrasts deserve emphasis. First, the \emph{polygon order} of the correction is
not uniform even within one direction: cancellation is carried by a quadrilateral at $q=5$ (no triangle
reaches a bigon there) but by a triangle at $q=7$. Second, there is a marked \emph{rigidity asymmetry}
between the directions: at the deficit members the minimal cochain is unique --- a cancelling polygon
must land exactly on an existing bigon --- while at the excess member fifty-five distinct minimal
cochains work, because creating a differential merely requires an immersed triangle through any
suitable crossing. Rank-matching alone thus pins the cochain at deficit members but not at excess
members; selecting \emph{the} cochain of the tangle at an excess member requires the (conjectural)
naturality data, not just the rank.

\subsection{Method and honesty}
Nothing on the pillowcase side was taken from \cite{Smith} as input. Both Lagrangians were
reconstructed from first principles --- the quaternionic representation theory, Smith's fiber-product
description of the Conway sum and his cut-and-paste resolution of the seam circles, and the
Herald--Kirk earring --- and validated against the published output of \cite{Smith} at $q=5$ (nine
generators, two bigons, rank $5$, and the worked resolution example) before anything new was computed.
The three registers are: (a) \emph{proved unconditionally} --- Theorem~\ref{thm:inat}; (b)
\emph{computed within the model} --- the naive ranks, the deficiency law at its five members, the
cochains, all by a self-contained program included with the source, with polygon counts by validated
winding-number tests; (c) \emph{conjectural} --- the faithfulness of the combinatorial model
\cite[Conj.~1.1]{CHKK} (under which the computed cochains are the values of the invariant-theoretic
ones), and the deficiency law beyond $q=13$. We prove no theorem about the analytic Atiyah--Floer
correspondence.

\medskip
Section~\ref{sec:inat} proves Theorem~\ref{thm:inat}. Section~\ref{sec:setup} assembles the
Lagrangians and records the validation gates and the naive-rank computations.
Section~\ref{sec:combinatorial} states the combinatorial Floer package.
Section~\ref{sec:compute} computes the three cochains. Section~\ref{sec:disc} discusses the law, the
threshold at $\det=3$, and the open problems.

\subsection*{Acknowledgements}
The pillowcase model and the geometry reconstructed here are due to Hedden--Herald--Kirk
\cite{HHK1,HHK2}, Cazassus--Herald--Kirk--Kotelskiy \cite{CHKK}, Herald--Kirk \cite{HK}, and Smith
\cite{Smith}; the closed-form Khovanov input is Manion's \cite{Manion}, and the Alexander polynomials
belong to Hironaka's family \cite{Hironaka}.

\section{The instanton rank of the family}\label{sec:inat}

\subsection{The Alexander polynomials}
\begin{proposition}\label{prop:alex}
For every odd $q\ge3$, the Alexander polynomial of $P(-2,3,q)$ is given, up to multiplication by
$\pm t^k$ and the substitution $t\mapsto-t$, by \eqref{eq:alex}. In particular all coefficients lie in
$\{0,\pm1\}$, exactly $q+2$ of them are nonzero, and
\[
   \ell(P(-2,3,q))=\sum_i|a_i(\Delta)|=q+2 .
\]
\end{proposition}

\begin{proof}
Apply the Conway skein relation $\nabla(L_+)-\nabla(L_-)=z\,\nabla(L_0)$ at a crossing of the
$q$-twist band of the standard pretzel diagram. Switching the crossing replaces $q$ by $q-2$;
smoothing it replaces $q$ by $q-1$ (a two-component pretzel link). Writing $a_q$, $b_q$ for the Conway
polynomials of the odd (knot) and even (link) members, the relation gives $a_q=a_{q-2}+sz\,b_{q-1}$
and $b_{q-1}=b_{q-3}+sz\,a_{q-2}$ with a fixed orientation sign $s$; eliminating $b$ yields the
three-term recursion
\begin{equation}\label{eq:cheby}
   a_{q+2}\;=\;(2+z^2)\,a_q-a_{q-2}\qquad(q\ \text{odd}),
\end{equation}
independent of $s$. Substituting $z^2=t-2+t^{-1}$, the multiplier is $t+t^{-1}$, so \eqref{eq:cheby}
is a Chebyshev-type recursion whose characteristic roots are $t^{\pm1}$; its solution is determined by
the seeds $q=3,5$, which are the torus knots $T(3,4)$, $T(3,5)$ with classical Alexander polynomials.
The normalization ambiguity (each $\Delta$ is defined up to $\pm t^k$, and this family satisfies
Hironaka's $t\mapsto-t$ twist \cite{Hironaka}) is fixed by validation: among the finitely many
normalizations of the seeds, exactly one makes \eqref{eq:cheby} reproduce
$\Delta_{P(-2,3,7)}$ --- Lehmer's polynomial, known independently \cite{Hironaka} --- and it does so
exactly, in all eleven coefficients. In that normalization one checks directly that the right side of
\eqref{eq:alex} satisfies \eqref{eq:cheby} (multiplication by $t+t^{-1}$ shifts the two-spike ends and
extends the middle block by one on each side; subtracting the previous member restores the pattern),
and agrees with the seeds; by induction \eqref{eq:alex} holds for all odd $q$. The coefficient count
is $2+2+(2(g-3)+1)=2g-1=q+2$.
\end{proof}

\begin{remark}
For $q=7$, \eqref{eq:alex} reads $t^5+t^4-t^2-t-1-t^{-1}-t^{-2}+t^{-4}+t^{-5}$: Lehmer's polynomial,
of Mahler measure $\approx1.17628$, smallest known. Hironaka \cite{Hironaka} proved that the
$(-2,3,q)$ pretzels realize the minimal-Mahler-measure family; Proposition~\ref{prop:alex} is a
self-contained derivation of exactly the data we need ($\Sigma|a_i|$), included so that
Theorem~\ref{thm:inat} does not rest on a translation of conventions.
\end{remark}

\subsection{The Khovanov bound and the squeeze}
Manion \cite[Thm.~1.1]{Manion} computes the reduced Khovanov homology of every non-quasi-alternating
$3$-strand pretzel. For $P(-p,q,r)$ with $p$ even, the total rank is $p^2+(q-p)(r-p)$; the knots
$P(-2,3,q)$, $q\ge3$ odd, are in the non-quasi-alternating range ($2\le3\le q$), so
\[
   u(P(-2,3,q))=\dim\Kh_r(P(-2,3,q))=4+(3-2)(q-2)=q+2 .
\]
(For the members with known Khovanov homology this agrees: $8_{19}$ has $\dim\Kh_r=5$ and $10_{124}$
has $7$.)

\begin{proof}[Proof of Theorem~\ref{thm:inat}]
The graded Euler characteristic of $\Inat$ is the Alexander polynomial \cite{KM1,Lim}, so
$\rk\Inat\ge\ell=q+2$ by Proposition~\ref{prop:alex}; the Kronheimer--Mrowka spectral sequence from
reduced Khovanov homology \cite{KM2} gives $\rk\Inat\le u=q+2$. Hence $\rk\Inat=q+2$.
\end{proof}

\begin{remark}
The same squeeze is how Smith identifies $\rk\Inat(P(-2,3,5))=7$ \cite[proof of Thm.~5.9]{Smith}; the
content added here is that Hironaka's and Manion's closed forms make it uniform in $q$. We also note
$\det P(-2,3,q)=|{-6}+3q-2q|=|q-6|$, which vanishes never and equals $1$ exactly for $q=5,7$: precisely
the members whose double branched cover is an integral homology sphere. This threshold reappears on
the symplectic side.
\end{remark}

\section{The Lagrangians of the family}\label{sec:setup}

\subsection{The pillowcase and the two curves}
We use $\SU$ as the unit quaternions; a traceless element is a purely imaginary unit. The traceless
character variety of the four-punctured sphere is the pillowcase of the introduction, with coordinates
$(\gamma,\theta)$, involution $\iota(\gamma,\theta)=(-\gamma,-\theta)$, and corners
$\{0,\pi\}^2$ \cite{Lin,HHK1}. We work on the double cover $T^2$, where curves lift to
$\iota$-invariant families; the count bookkeeping is \S\ref{ss:lift}. A rational tangle $Q_r$ has for
its character variety a straight line of slope $r$ through the corners \cite{HHK1}. Two operations
build the family's curves:
\begin{itemize}
\item \emph{Conway sum.} On the pillowcase, $T_1+T_2$ is the fiber product over $\gamma$: the
$\theta$-coordinates add, and over each seam $\gamma\in\{0,\pi\}$ a circle of reducibles appears when
both summands are non-abelian there \cite[Thm.~4.22]{Smith}. Perturbing resolves each circle by a
diagonal cut-and-paste \cite[Thm.~4.23]{Smith}, adding one self-intersection per circle.
\item \emph{Earring.} $\Qh{r}$ replaces the arc of $Q_r$ by the Herald--Kirk figure-eight: the doubled
arc closing through the corner folds, with one pinch \cite[Def.~6.6]{HK}; its bounding cochain
vanishes \cite[Lem.~5.6]{Smith}.
\end{itemize}
For the decomposition \eqref{eq:family} the $-2$ band is constant, so
\textbf{red} $=\Rnat(\Qh{-1/2})$ is \emph{independent of $q$} (one immersed circle, one pinch), while
\textbf{blue} $=\Rp_t(Q_{1/3}+Q_{1/q})$ varies: two seams, four resolved circles, a single immersed
circle whose self-intersection count grows with $q$ (forty at $q=5$, eighty-two at $q=7$, two hundred
twenty-five at $q=11$). We require $\gcd(q,3)=1$ (else corner circles appear); this excludes $q=9,15,\dots$
from the pillowcase analysis but not from Theorem~\ref{thm:inat}.

\begin{figure}[ht]
\centering
\begin{tikzpicture}[scale=1.35]
% --- Figure 1 curves, generated by pillowcase/make_figure.py (inlined) ---
% AUTO-GENERATED by pillowcase/make_figure.py -- the REAL q=5 curves.
%% blue folded into 52 pieces; red (both lifts) into 10 pieces.
\draw[thick] (0,0) rectangle (3.14159,6.28319);
\foreach \y in {0,3.14159,6.28319}{\fill (-0.035,\y-0.035) rectangle (0.035,\y+0.035); \fill (3.14159-0.035,\y-0.035) rectangle (3.14159+0.035,\y+0.035);}
\node[below] at (0,0) {\footnotesize $(0,0)$};
\node[below] at (3.1416,0) {\footnotesize $(\pi,0)$};
\node[left] at (0,6.2832) {\footnotesize $(0,2\pi)$};
\node[right] at (3.1416,6.2832) {\footnotesize $(\pi,2\pi)$};
\draw[->] (-0.15,0)--(3.4916,0) node[right] {\footnotesize $\gamma$};
\draw[->] (0,-0.15)--(0,6.6832) node[above] {\footnotesize $\theta$};
\draw[blue,line width=0.55pt] (0.0000,5.4454) -- (0.1571,5.5292) -- (0.3142,5.6130) -- (0.4712,5.6968) -- (0.6283,5.7805) -- (0.7854,5.8643) -- (0.9425,5.9481) -- (1.0996,6.0319) -- (1.2566,6.1156) -- (1.4137,6.1994) -- (1.4923,6.2413);
\draw[blue,line width=0.55pt] (1.5708,0.0000) -- (1.7279,0.0838) -- (1.8850,0.1676) -- (2.0420,0.2513) -- (2.1991,0.3351) -- (2.3562,0.4189) -- (2.5133,0.5027) -- (2.6704,0.5864) -- (2.8274,0.6702) -- (2.9845,0.7540) -- (3.0631,0.7959);
\draw[blue,line width=0.55pt] (3.1336,0.8836) -- (3.1150,0.9948) -- (3.1000,1.1126) -- (3.0923,1.2305) -- (3.0926,1.3352) -- (3.0974,1.4137) -- (3.1056,1.4923) -- (3.1186,1.5839) -- (3.1411,1.7148);
\draw[blue,line width=0.55pt] (3.1402,4.5553) -- (3.1221,4.4113) -- (3.1092,4.2935) -- (3.1012,4.2019) -- (3.0937,4.0710) -- (3.0916,3.9532) -- (3.0947,3.8223) -- (3.1030,3.6914) -- (3.1173,3.5474) -- (3.1341,3.4099) -- (3.0631,3.3091) -- (2.9060,3.2254) -- (2.7489,3.1416) -- (2.5918,3.0578) -- (2.4347,2.9740) -- (2.2777,2.8903) -- (2.1206,2.8065) -- (1.9635,2.7227) -- (1.8064,2.6389) -- (1.6493,2.5552) -- (1.4923,2.4714) -- (1.3352,2.3876) -- (1.1781,2.3038) -- (1.0210,2.2201) -- (0.8639,2.1363) -- (0.7069,2.0525) -- (0.5498,1.9687) -- (0.3927,1.8850) -- (0.2356,1.8012) -- (0.0785,1.7174) -- (0.0135,1.6205) -- (0.0299,1.5420) -- (0.0392,1.4713) -- (0.0418,1.4085) -- (0.0394,1.3535) -- (0.0339,1.3064) -- (0.0258,1.2593) -- (0.0004,1.1493);
\draw[blue,line width=0.55pt] (0.0011,5.1417) -- (0.0163,5.2281) -- (0.0338,5.3538) -- (0.0411,5.4559) -- (0.0412,5.5423) -- (0.0363,5.6208) -- (0.0273,5.6994) -- (0.0126,5.7936);
\draw[blue,line width=0.55pt] (0.0785,5.9062) -- (0.2356,5.9900) -- (0.3927,6.0737) -- (0.5498,6.1575) -- (0.7069,6.2413);
\draw[blue,line width=0.55pt] (0.7854,0.0000) -- (0.9425,0.0838) -- (1.0996,0.1676) -- (1.2566,0.2513) -- (1.4137,0.3351) -- (1.5708,0.4189) -- (1.7279,0.5027) -- (1.8850,0.5864) -- (2.0420,0.6702) -- (2.1991,0.7540) -- (2.3562,0.8378) -- (2.5133,0.9215) -- (2.6704,1.0053) -- (2.8274,1.0891) -- (2.9845,1.1729) -- (3.0631,1.2147);
\draw[blue,line width=0.55pt] (3.1416,5.0265) -- (2.9845,4.9428) -- (2.8274,4.8590) -- (2.6704,4.7752) -- (2.5133,4.6914) -- (2.3562,4.6077) -- (2.1991,4.5239) -- (2.0420,4.4401) -- (1.8850,4.3563) -- (1.7279,4.2726) -- (1.5708,4.1888) -- (1.4137,4.1050) -- (1.2566,4.0212) -- (1.0996,3.9375) -- (0.9425,3.8537) -- (0.7854,3.7699) -- (0.6283,3.6861) -- (0.4712,3.6024) -- (0.3142,3.5186) -- (0.1571,3.4348) -- (0.0785,3.3929);
\draw[blue,line width=0.55pt] (0.0075,3.4099) -- (0.0243,3.5474) -- (0.0385,3.6914) -- (0.0469,3.8223) -- (0.0500,3.9532) -- (0.0479,4.0710) -- (0.0404,4.2019) -- (0.0324,4.2935) -- (0.0194,4.4113) -- (0.0014,4.5553);
\draw[blue,line width=0.55pt] (0.0005,1.7148) -- (0.0229,1.5839) -- (0.0360,1.4923) -- (0.0442,1.4137) -- (0.0489,1.3352) -- (0.0493,1.2305) -- (0.0416,1.1126) -- (0.0266,0.9948) -- (0.0080,0.8836);
\draw[blue,line width=0.55pt] (0.0785,0.8796) -- (0.2356,0.9634) -- (0.3927,1.0472) -- (0.5498,1.1310) -- (0.7069,1.2147) -- (0.8639,1.2985) -- (1.0210,1.3823) -- (1.1781,1.4661) -- (1.3352,1.5499) -- (1.4923,1.6336) -- (1.6493,1.7174) -- (1.8064,1.8012) -- (1.9635,1.8850) -- (2.1206,1.9687) -- (2.2777,2.0525) -- (2.4347,2.1363) -- (2.5918,2.2201) -- (2.7489,2.3038) -- (2.9060,2.3876) -- (3.0631,2.4714);
\draw[blue,line width=0.55pt] (3.1416,3.7699) -- (2.9845,3.6861) -- (2.8274,3.6024) -- (2.6704,3.5186) -- (2.5133,3.4348) -- (2.3562,3.3510) -- (2.1991,3.2673) -- (2.0420,3.1835) -- (1.8850,3.0997) -- (1.7279,3.0159) -- (1.5708,2.9322) -- (1.4137,2.8484) -- (1.2566,2.7646) -- (1.0996,2.6808) -- (0.9425,2.5970) -- (0.7854,2.5133) -- (0.6283,2.4295) -- (0.4712,2.3457) -- (0.3142,2.2619) -- (0.1571,2.1782) -- (0.0785,2.1363);
\draw[blue,line width=0.55pt] (0.0000,4.1888) -- (0.1571,4.2726) -- (0.3142,4.3563) -- (0.4712,4.4401) -- (0.6283,4.5239) -- (0.7854,4.6077) -- (0.9425,4.6914) -- (1.0996,4.7752) -- (1.2566,4.8590) -- (1.4137,4.9428) -- (1.5708,5.0265) -- (1.7279,5.1103) -- (1.8850,5.1941) -- (2.0420,5.2779) -- (2.1991,5.3617) -- (2.3562,5.4454) -- (2.5133,5.5292) -- (2.6704,5.6130) -- (2.8274,5.6968) -- (2.9845,5.7805) -- (3.0631,5.8224);
\draw[blue,line width=0.55pt] (3.1258,5.7936) -- (3.1072,5.6994) -- (3.0959,5.6208) -- (3.0898,5.5423) -- (3.0898,5.4559) -- (3.0936,5.4009) -- (3.1075,5.2988) -- (3.1211,5.2281) -- (3.1402,5.1417);
\draw[blue,line width=0.55pt] (3.1411,1.1493) -- (3.1174,1.2278) -- (3.1036,1.2828) -- (3.0950,1.3299) -- (3.0900,1.3771) -- (3.0896,1.4399) -- (3.0941,1.4870) -- (3.1040,1.5420) -- (3.1247,1.6205) -- (3.0631,1.6336) -- (2.9060,1.5499) -- (2.7489,1.4661) -- (2.5918,1.3823) -- (2.4347,1.2985) -- (2.2777,1.2147) -- (2.1206,1.1310) -- (1.9635,1.0472) -- (1.8064,0.9634) -- (1.6493,0.8796) -- (1.4923,0.7959) -- (1.3352,0.7121) -- (1.1781,0.6283) -- (1.0210,0.5445) -- (0.8639,0.4608) -- (0.7069,0.3770) -- (0.5498,0.2932) -- (0.3927,0.2094) -- (0.2356,0.1257) -- (0.0785,0.0419) -- (0.0785,0.0419) -- (0.2356,0.1257) -- (0.3927,0.2094) -- (0.5498,0.2932) -- (0.7069,0.3770) -- (0.8639,0.4608) -- (1.0210,0.5445) -- (1.1781,0.6283) -- (1.3352,0.7121) -- (1.4923,0.7959) -- (1.6493,0.8796) -- (1.8064,0.9634) -- (1.9635,1.0472) -- (2.1206,1.1310) -- (2.2777,1.2147) -- (2.4347,1.2985) -- (2.5918,1.3823) -- (2.7489,1.4661) -- (2.9060,1.5499) -- (3.0631,1.6336);
\draw[blue,line width=0.55pt] (3.1247,1.6205) -- (3.1040,1.5420) -- (3.0941,1.4870) -- (3.0896,1.4399) -- (3.0900,1.3771) -- (3.0950,1.3299) -- (3.1036,1.2828) -- (3.1174,1.2278) -- (3.1411,1.1493);
\draw[blue,line width=0.55pt] (3.1402,5.1417) -- (3.1211,5.2281) -- (3.1075,5.2988) -- (3.0936,5.4009) -- (3.0898,5.4559) -- (3.0898,5.5423) -- (3.0959,5.6208) -- (3.1072,5.6994) -- (3.1258,5.7936) -- (3.0631,5.8224) -- (2.9060,5.7386) -- (2.7489,5.6549) -- (2.5918,5.5711) -- (2.4347,5.4873) -- (2.2777,5.4035) -- (2.1206,5.3198) -- (1.9635,5.2360) -- (1.8064,5.1522) -- (1.6493,5.0684) -- (1.4923,4.9847) -- (1.3352,4.9009) -- (1.1781,4.8171) -- (1.0210,4.7333) -- (0.8639,4.6496) -- (0.7069,4.5658) -- (0.5498,4.4820) -- (0.3927,4.3982) -- (0.2356,4.3145) -- (0.0785,4.2307);
\draw[blue,line width=0.55pt] (0.0000,2.0944) -- (0.1571,2.1782) -- (0.3142,2.2619) -- (0.4712,2.3457) -- (0.6283,2.4295) -- (0.7854,2.5133) -- (0.9425,2.5970) -- (1.0996,2.6808) -- (1.2566,2.7646) -- (1.4137,2.8484) -- (1.5708,2.9322) -- (1.7279,3.0159) -- (1.8850,3.0997) -- (2.0420,3.1835) -- (2.1991,3.2673) -- (2.3562,3.3510) -- (2.5133,3.4348) -- (2.6704,3.5186) -- (2.8274,3.6024) -- (2.9845,3.6861) -- (3.0631,3.7280);
\draw[blue,line width=0.55pt] (3.1416,2.5133) -- (2.9845,2.4295) -- (2.8274,2.3457) -- (2.6704,2.2619) -- (2.5133,2.1782) -- (2.3562,2.0944) -- (2.1991,2.0106) -- (2.0420,1.9268) -- (1.8850,1.8431) -- (1.7279,1.7593) -- (1.5708,1.6755) -- (1.4137,1.5917) -- (1.2566,1.5080) -- (1.0996,1.4242) -- (0.9425,1.3404) -- (0.7854,1.2566) -- (0.6283,1.1729) -- (0.4712,1.0891) -- (0.3142,1.0053) -- (0.1571,0.9215) -- (0.0785,0.8796);
\draw[blue,line width=0.55pt] (0.0080,0.8836) -- (0.0266,0.9948) -- (0.0416,1.1126) -- (0.0493,1.2305) -- (0.0489,1.3352) -- (0.0442,1.4137) -- (0.0360,1.4923) -- (0.0229,1.5839) -- (0.0005,1.7148);
\draw[blue,line width=0.55pt] (0.0014,4.5553) -- (0.0194,4.4113) -- (0.0324,4.2935) -- (0.0404,4.2019) -- (0.0479,4.0710) -- (0.0500,3.9532) -- (0.0469,3.8223) -- (0.0385,3.6914) -- (0.0243,3.5474) -- (0.0075,3.4099) -- (0.0785,3.3929) -- (0.2356,3.4767) -- (0.3927,3.5605) -- (0.5498,3.6442) -- (0.7069,3.7280) -- (0.8639,3.8118) -- (1.0210,3.8956) -- (1.1781,3.9794) -- (1.3352,4.0631) -- (1.4923,4.1469) -- (1.6493,4.2307) -- (1.8064,4.3145) -- (1.9635,4.3982) -- (2.1206,4.4820) -- (2.2777,4.5658) -- (2.4347,4.6496) -- (2.5918,4.7333) -- (2.7489,4.8171) -- (2.9060,4.9009) -- (3.0631,4.9847);
\draw[blue,line width=0.55pt] (3.1416,1.2566) -- (2.9845,1.1729) -- (2.8274,1.0891) -- (2.6704,1.0053) -- (2.5133,0.9215) -- (2.3562,0.8378) -- (2.1991,0.7540) -- (2.0420,0.6702) -- (1.8850,0.5864) -- (1.7279,0.5027) -- (1.5708,0.4189) -- (1.4137,0.3351) -- (1.2566,0.2513) -- (1.0996,0.1676) -- (0.9425,0.0838) -- (0.7854,0.0000);
\draw[blue,line width=0.55pt] (0.7069,6.2413) -- (0.5498,6.1575) -- (0.3927,6.0737) -- (0.2356,5.9900) -- (0.0785,5.9062);
\draw[blue,line width=0.55pt] (0.0126,5.7936) -- (0.0273,5.6994) -- (0.0363,5.6208) -- (0.0412,5.5423) -- (0.0411,5.4559) -- (0.0338,5.3538) -- (0.0163,5.2281) -- (0.0011,5.1417);
\draw[blue,line width=0.55pt] (0.0004,1.1493) -- (0.0258,1.2593) -- (0.0339,1.3064) -- (0.0394,1.3535) -- (0.0418,1.4085) -- (0.0392,1.4713) -- (0.0299,1.5420) -- (0.0135,1.6205) -- (0.0785,1.7174) -- (0.2356,1.8012) -- (0.3927,1.8850) -- (0.5498,1.9687) -- (0.7069,2.0525) -- (0.8639,2.1363) -- (1.0210,2.2201) -- (1.1781,2.3038) -- (1.3352,2.3876) -- (1.4923,2.4714) -- (1.6493,2.5552) -- (1.8064,2.6389) -- (1.9635,2.7227) -- (2.1206,2.8065) -- (2.2777,2.8903) -- (2.4347,2.9740) -- (2.5918,3.0578) -- (2.7489,3.1416) -- (2.9060,3.2254) -- (3.0631,3.3091);
\draw[blue,line width=0.55pt] (3.1341,3.4099) -- (3.1173,3.5474) -- (3.1030,3.6914) -- (3.0947,3.8223) -- (3.0916,3.9532) -- (3.0937,4.0710) -- (3.1012,4.2019) -- (3.1092,4.2935) -- (3.1221,4.4113) -- (3.1402,4.5553);
\draw[blue,line width=0.55pt] (3.1411,1.7148) -- (3.1186,1.5839) -- (3.1056,1.4923) -- (3.0974,1.4137) -- (3.0926,1.3352) -- (3.0923,1.2305) -- (3.1000,1.1126) -- (3.1150,0.9948) -- (3.1336,0.8836) -- (3.0631,0.7959) -- (2.9060,0.7121) -- (2.7489,0.6283) -- (2.5918,0.5445) -- (2.4347,0.4608) -- (2.2777,0.3770) -- (2.1206,0.2932) -- (1.9635,0.2094) -- (1.8064,0.1257) -- (1.6493,0.0419) -- (1.5708,0.0000);
\draw[blue,line width=0.55pt] (1.4923,6.2413) -- (1.3352,6.1575) -- (1.1781,6.0737) -- (1.0210,5.9900) -- (0.8639,5.9062) -- (0.7069,5.8224) -- (0.5498,5.7386) -- (0.3927,5.6549) -- (0.2356,5.5711) -- (0.0785,5.4873);
\draw[blue,line width=0.55pt] (0.0050,5.3800) -- (0.0151,5.2491) -- (0.0239,5.1051) -- (0.0291,4.9742) -- (0.0310,4.8433) -- (0.0293,4.7189) -- (0.0251,4.5946) -- (0.0201,4.5029) -- (0.0121,4.3851) -- (0.0008,4.2412);
\draw[blue,line width=0.55pt] (0.0067,2.1140) -- (0.0183,2.2318) -- (0.0274,2.3562) -- (0.0310,2.4871) -- (0.0291,2.5918) -- (0.0221,2.7096) -- (0.0100,2.8405) -- (0.0000,2.9322) -- (0.1571,3.0159) -- (0.3142,3.0997) -- (0.4712,3.1835) -- (0.6283,3.2673) -- (0.7854,3.3510) -- (0.9425,3.4348) -- (1.0996,3.5186) -- (1.2566,3.6024) -- (1.4137,3.6861) -- (1.5708,3.7699) -- (1.7279,3.8537) -- (1.8850,3.9375) -- (2.0420,4.0212) -- (2.1991,4.1050) -- (2.3562,4.1888) -- (2.5133,4.2726) -- (2.6704,4.3563) -- (2.8274,4.4401) -- (2.9845,4.5239) -- (3.0631,4.5658);
\draw[blue,line width=0.55pt] (3.1161,4.6784) -- (3.0861,4.7726) -- (3.0679,4.8511) -- (3.0580,4.9297) -- (3.0569,4.9925) -- (3.0602,5.0396) -- (3.0682,5.0946) -- (3.0783,5.1417) -- (3.0958,5.2046) -- (3.1239,5.2870) -- (3.1393,5.3302);
\draw[blue,line width=0.55pt] (3.1408,0.9451) -- (3.1026,0.8666) -- (3.0804,0.8116) -- (3.0664,0.7645) -- (3.0584,0.7173) -- (3.0566,0.6859) -- (3.0578,0.6545) -- (3.0619,0.6231) -- (3.0709,0.5838) -- (3.0868,0.5367) -- (3.1143,0.4739) -- (3.0631,0.3770) -- (2.9060,0.2932) -- (2.7489,0.2094) -- (2.5918,0.1257) -- (2.4347,0.0419) -- (2.3562,0.0000);
\draw[blue,line width=0.55pt] (2.2777,6.2413) -- (2.1206,6.1575) -- (1.9635,6.0737) -- (1.8064,5.9900) -- (1.6493,5.9062) -- (1.4923,5.8224) -- (1.3352,5.7386) -- (1.1781,5.6549) -- (1.0210,5.5711) -- (0.8639,5.4873) -- (0.7069,5.4035) -- (0.5498,5.3198) -- (0.3927,5.2360) -- (0.2356,5.1522) -- (0.0785,5.0684);
\draw[blue,line width=0.55pt] (0.0000,1.2566) -- (0.1571,1.3404) -- (0.3142,1.4242) -- (0.4712,1.5080) -- (0.6283,1.5917) -- (0.7854,1.6755) -- (0.9425,1.7593) -- (1.0996,1.8431) -- (1.2566,1.9268) -- (1.4137,2.0106) -- (1.5708,2.0944) -- (1.7279,2.1782) -- (1.8850,2.2619) -- (2.0420,2.3457) -- (2.1991,2.4295) -- (2.3562,2.5133) -- (2.5133,2.5970) -- (2.6704,2.6808) -- (2.8274,2.7646) -- (2.9845,2.8484) -- (3.0631,2.8903);
\draw[blue,line width=0.55pt] (3.1366,2.8863) -- (3.1251,2.7751) -- (3.1158,2.6573) -- (3.1110,2.5395) -- (3.1112,2.4347) -- (3.1193,2.2777) -- (3.1274,2.1860) -- (3.1349,2.1140);
\draw[blue,line width=0.55pt] (3.1408,4.2412) -- (3.1295,4.3851) -- (3.1215,4.5029) -- (3.1165,4.5946) -- (3.1123,4.7189) -- (3.1106,4.8433) -- (3.1125,4.9742) -- (3.1177,5.1051) -- (3.1265,5.2491) -- (3.1366,5.3800) -- (3.0631,5.4035) -- (2.9060,5.3198) -- (2.7489,5.2360) -- (2.5918,5.1522) -- (2.4347,5.0684) -- (2.2777,4.9847) -- (2.1206,4.9009) -- (1.9635,4.8171) -- (1.8064,4.7333) -- (1.6493,4.6496) -- (1.4923,4.5658) -- (1.3352,4.4820) -- (1.1781,4.3982) -- (1.0210,4.3145) -- (0.8639,4.2307) -- (0.7069,4.1469) -- (0.5498,4.0631) -- (0.3927,3.9794) -- (0.2356,3.8956) -- (0.0785,3.8118);
\draw[blue,line width=0.55pt] (0.0000,2.5133) -- (0.1571,2.5970) -- (0.3142,2.6808) -- (0.4712,2.7646) -- (0.6283,2.8484) -- (0.7854,2.9322) -- (0.9425,3.0159) -- (1.0996,3.0997) -- (1.2566,3.1835) -- (1.4137,3.2673) -- (1.5708,3.3510) -- (1.7279,3.4348) -- (1.8850,3.5186) -- (2.0420,3.6024) -- (2.1991,3.6861) -- (2.3562,3.7699) -- (2.5133,3.8537) -- (2.6704,3.9375) -- (2.8274,4.0212) -- (2.9845,4.1050) -- (3.0631,4.1469);
\draw[blue,line width=0.55pt] (3.1416,2.0944) -- (2.9845,2.0106) -- (2.8274,1.9268) -- (2.6704,1.8431) -- (2.5133,1.7593) -- (2.3562,1.6755) -- (2.1991,1.5917) -- (2.0420,1.5080) -- (1.8850,1.4242) -- (1.7279,1.3404) -- (1.5708,1.2566) -- (1.4137,1.1729) -- (1.2566,1.0891) -- (1.0996,1.0053) -- (0.9425,0.9215) -- (0.7854,0.8378) -- (0.6283,0.7540) -- (0.4712,0.6702) -- (0.3142,0.5864) -- (0.1571,0.5027) -- (0.0785,0.4608);
\draw[blue,line width=0.55pt] (0.0217,0.4739) -- (0.0482,0.5524) -- (0.0608,0.6074) -- (0.0665,0.6545) -- (0.0661,0.7173) -- (0.0597,0.7645) -- (0.0486,0.8116) -- (0.0310,0.8666) -- (0.0006,0.9451);
\draw[blue,line width=0.55pt] (0.0018,5.3302) -- (0.0263,5.2438) -- (0.0437,5.1732) -- (0.0546,5.1182) -- (0.0647,5.0396) -- (0.0672,4.9925) -- (0.0664,4.9297) -- (0.0585,4.8511) -- (0.0440,4.7726) -- (0.0202,4.6784) -- (0.0785,4.6496) -- (0.2356,4.7333) -- (0.3927,4.8171) -- (0.5498,4.9009) -- (0.7069,4.9847) -- (0.8639,5.0684) -- (1.0210,5.1522) -- (1.1781,5.2360) -- (1.3352,5.3198) -- (1.4923,5.4035) -- (1.6493,5.4873) -- (1.8064,5.5711) -- (1.9635,5.6549) -- (2.1206,5.7386) -- (2.2777,5.8224) -- (2.4347,5.9062) -- (2.5918,5.9900) -- (2.7489,6.0737) -- (2.9060,6.1575) -- (3.0631,6.2413) -- (3.0631,6.2413) -- (2.9060,6.1575) -- (2.7489,6.0737) -- (2.5918,5.9900) -- (2.4347,5.9062) -- (2.2777,5.8224) -- (2.1206,5.7386) -- (1.9635,5.6549) -- (1.8064,5.5711) -- (1.6493,5.4873) -- (1.4923,5.4035) -- (1.3352,5.3198) -- (1.1781,5.2360) -- (1.0210,5.1522) -- (0.8639,5.0684) -- (0.7069,4.9847) -- (0.5498,4.9009) -- (0.3927,4.8171) -- (0.2356,4.7333) -- (0.0785,4.6496);
\draw[blue,line width=0.55pt] (0.0202,4.6784) -- (0.0440,4.7726) -- (0.0585,4.8511) -- (0.0664,4.9297) -- (0.0672,4.9925) -- (0.0647,5.0396) -- (0.0546,5.1182) -- (0.0437,5.1732) -- (0.0263,5.2438) -- (0.0018,5.3302);
\draw[blue,line width=0.55pt] (0.0006,0.9451) -- (0.0310,0.8666) -- (0.0486,0.8116) -- (0.0597,0.7645) -- (0.0661,0.7173) -- (0.0665,0.6545) -- (0.0608,0.6074) -- (0.0482,0.5524) -- (0.0217,0.4739) -- (0.0785,0.4608) -- (0.2356,0.5445) -- (0.3927,0.6283) -- (0.5498,0.7121) -- (0.7069,0.7959) -- (0.8639,0.8796) -- (1.0210,0.9634) -- (1.1781,1.0472) -- (1.3352,1.1310) -- (1.4923,1.2147) -- (1.6493,1.2985) -- (1.8064,1.3823) -- (1.9635,1.4661) -- (2.1206,1.5499) -- (2.2777,1.6336) -- (2.4347,1.7174) -- (2.5918,1.8012) -- (2.7489,1.8850) -- (2.9060,1.9687) -- (3.0631,2.0525);
\draw[blue,line width=0.55pt] (3.1416,4.1888) -- (2.9845,4.1050) -- (2.8274,4.0212) -- (2.6704,3.9375) -- (2.5133,3.8537) -- (2.3562,3.7699) -- (2.1991,3.6861) -- (2.0420,3.6024) -- (1.8850,3.5186) -- (1.7279,3.4348) -- (1.5708,3.3510) -- (1.4137,3.2673) -- (1.2566,3.1835) -- (1.0996,3.0997) -- (0.9425,3.0159) -- (0.7854,2.9322) -- (0.6283,2.8484) -- (0.4712,2.7646) -- (0.3142,2.6808) -- (0.1571,2.5970) -- (0.0785,2.5552);
\draw[blue,line width=0.55pt] (0.0000,3.7699) -- (0.1571,3.8537) -- (0.3142,3.9375) -- (0.4712,4.0212) -- (0.6283,4.1050) -- (0.7854,4.1888) -- (0.9425,4.2726) -- (1.0996,4.3563) -- (1.2566,4.4401) -- (1.4137,4.5239) -- (1.5708,4.6077) -- (1.7279,4.6914) -- (1.8850,4.7752) -- (2.0420,4.8590) -- (2.1991,4.9428) -- (2.3562,5.0265) -- (2.5133,5.1103) -- (2.6704,5.1941) -- (2.8274,5.2779) -- (2.9845,5.3617) -- (3.0631,5.4035);
\draw[blue,line width=0.55pt] (3.1366,5.3800) -- (3.1265,5.2491) -- (3.1177,5.1051) -- (3.1125,4.9742) -- (3.1106,4.8433) -- (3.1123,4.7189) -- (3.1165,4.5946) -- (3.1215,4.5029) -- (3.1295,4.3851) -- (3.1408,4.2412);
\draw[blue,line width=0.55pt] (3.1349,2.1140) -- (3.1233,2.2318) -- (3.1142,2.3562) -- (3.1106,2.4871) -- (3.1125,2.5918) -- (3.1195,2.7096) -- (3.1316,2.8405) -- (3.1416,2.9322) -- (2.9845,2.8484) -- (2.8274,2.7646) -- (2.6704,2.6808) -- (2.5133,2.5970) -- (2.3562,2.5133) -- (2.1991,2.4295) -- (2.0420,2.3457) -- (1.8850,2.2619) -- (1.7279,2.1782) -- (1.5708,2.0944) -- (1.4137,2.0106) -- (1.2566,1.9268) -- (1.0996,1.8431) -- (0.9425,1.7593) -- (0.7854,1.6755) -- (0.6283,1.5917) -- (0.4712,1.5080) -- (0.3142,1.4242) -- (0.1571,1.3404) -- (0.0785,1.2985);
\draw[blue,line width=0.55pt] (0.0000,5.0265) -- (0.1571,5.1103) -- (0.3142,5.1941) -- (0.4712,5.2779) -- (0.6283,5.3617) -- (0.7854,5.4454) -- (0.9425,5.5292) -- (1.0996,5.6130) -- (1.2566,5.6968) -- (1.4137,5.7805) -- (1.5708,5.8643) -- (1.7279,5.9481) -- (1.8850,6.0319) -- (2.0420,6.1156) -- (2.1991,6.1994) -- (2.2777,6.2413);
\draw[blue,line width=0.55pt] (2.3562,0.0000) -- (2.5133,0.0838) -- (2.6704,0.1676) -- (2.8274,0.2513) -- (2.9845,0.3351) -- (3.0631,0.3770);
\draw[blue,line width=0.55pt] (3.1143,0.4739) -- (3.0868,0.5367) -- (3.0709,0.5838) -- (3.0619,0.6231) -- (3.0578,0.6545) -- (3.0566,0.6859) -- (3.0584,0.7173) -- (3.0664,0.7645) -- (3.0804,0.8116) -- (3.1026,0.8666) -- (3.1408,0.9451);
\draw[blue,line width=0.55pt] (3.1393,5.3302) -- (3.1085,5.2438) -- (3.0866,5.1732) -- (3.0729,5.1182) -- (3.0642,5.0711) -- (3.0581,5.0161) -- (3.0566,4.9690) -- (3.0618,4.8904) -- (3.0761,4.8119) -- (3.1003,4.7255) -- (3.1416,4.6077) -- (2.9845,4.5239) -- (2.8274,4.4401) -- (2.6704,4.3563) -- (2.5133,4.2726) -- (2.3562,4.1888) -- (2.1991,4.1050) -- (2.0420,4.0212) -- (1.8850,3.9375) -- (1.7279,3.8537) -- (1.5708,3.7699) -- (1.4137,3.6861) -- (1.2566,3.6024) -- (1.0996,3.5186) -- (0.9425,3.4348) -- (0.7854,3.3510) -- (0.6283,3.2673) -- (0.4712,3.1835) -- (0.3142,3.0997) -- (0.1571,3.0159) -- (0.0785,2.9740);
\draw[blue,line width=0.55pt] (0.0050,2.8863) -- (0.0165,2.7751) -- (0.0258,2.6573) -- (0.0306,2.5395) -- (0.0303,2.4347) -- (0.0223,2.2777) -- (0.0142,2.1860) -- (0.0067,2.1140);
\draw[blue,line width=0.55pt] (0.0008,4.2412) -- (0.0121,4.3851) -- (0.0201,4.5029) -- (0.0251,4.5946) -- (0.0293,4.7189) -- (0.0310,4.8433) -- (0.0291,4.9742) -- (0.0239,5.1051) -- (0.0151,5.2491) -- (0.0050,5.3800) -- (0.0000,5.4454);
\draw[red,line width=0.45pt] (0.3012,0.2526) -- (0.3699,0.2853) -- (0.4385,0.3180) -- (0.5073,0.3505) -- (0.5761,0.3829) -- (0.6450,0.4152) -- (0.7139,0.4474) -- (0.7828,0.4796) -- (0.8517,0.5119) -- (0.9261,0.5462) -- (1.0004,0.5806) -- (1.0748,0.6149) -- (1.1492,0.6493) -- (1.2264,0.6845) -- (1.3036,0.7197) -- (1.3808,0.7550) -- (1.4580,0.7902) -- (1.5273,0.8216) -- (1.5967,0.8529) -- (1.6660,0.8843) -- (1.7353,0.9157) -- (1.8101,0.9492) -- (1.8849,0.9828) -- (1.9597,1.0164) -- (2.0344,1.0499) -- (2.1093,1.0834) -- (2.1841,1.1168) -- (2.2589,1.1502) -- (2.3338,1.1837) -- (2.4076,1.2165) -- (2.4814,1.2494) -- (2.5552,1.2823) -- (2.6290,1.3152) -- (2.7028,1.3481) -- (2.7766,1.3810) -- (2.8504,1.4139) -- (2.9242,1.4468) -- (2.9980,1.4797) -- (3.0718,1.5125) -- (3.1395,1.5429);
\draw[red,line width=0.45pt] (3.0760,4.7100) -- (3.0084,4.6797) -- (2.9407,4.6494) -- (2.8730,4.6191) -- (2.8053,4.5887) -- (2.7342,4.5567) -- (2.6630,4.5246) -- (2.5919,4.4925) -- (2.5279,4.4635) -- (2.4640,4.4345) -- (2.4000,4.4055) -- (2.3361,4.3763) -- (2.2722,4.3471) -- (2.2083,4.3180) -- (2.1480,4.2903) -- (2.0878,4.2626) -- (2.0275,4.2349) -- (1.9567,4.2021) -- (1.8859,4.1693) -- (1.8151,4.1364) -- (1.7480,4.1050) -- (1.6809,4.0736) -- (1.6137,4.0422) -- (1.5467,4.0106) -- (1.4797,3.9790) -- (1.4127,3.9473) -- (1.3493,3.9171) -- (1.2860,3.8869) -- (1.2226,3.8566) -- (1.1559,3.8245) -- (1.0891,3.7923) -- (1.0224,3.7601) -- (0.9593,3.7294) -- (0.8961,3.6987) -- (0.8330,3.6679) -- (0.7701,3.6369) -- (0.7071,3.6059) -- (0.6441,3.5750) -- (0.5813,3.5437) -- (0.5184,3.5124) -- (0.4556,3.4812) -- (0.3929,3.4497) -- (0.3301,3.4181) -- (0.2674,3.3866) -- (0.2014,3.3531) -- (0.1353,3.3195) -- (0.0693,3.2859) -- (0.0068,3.2539) -- (0.0556,3.0614) -- (0.1181,3.0934) -- (0.1838,3.1275) -- (0.2496,3.1616) -- (0.3154,3.1958) -- (0.3810,3.2301) -- (0.4467,3.2645) -- (0.5123,3.2989) -- (0.5813,3.3354) -- (0.6502,3.3719) -- (0.7192,3.4084) -- (0.7880,3.4451) -- (0.8568,3.4818) -- (0.9257,3.5186) -- (0.9943,3.5556) -- (1.0630,3.5926) -- (1.1317,3.6296) -- (1.1900,3.6612) -- (1.2483,3.6928) -- (1.3066,3.7245) -- (1.3683,3.7581) -- (1.4299,3.7918) -- (1.4916,3.8254) -- (1.5532,3.8592) -- (1.6147,3.8930) -- (1.6763,3.9268) -- (1.7447,3.9645) -- (1.8130,4.0022) -- (1.8813,4.0399) -- (1.9551,4.0808) -- (2.0288,4.1217) -- (2.1025,4.1626) -- (2.1763,4.2035) -- (2.2500,4.2443) -- (2.3267,4.2871) -- (2.4035,4.3298) -- (2.4802,4.3725) -- (2.5569,4.4152) -- (2.6337,4.4579) -- (2.7104,4.5006) -- (2.7871,4.5433) -- (2.8639,4.5860) -- (2.9406,4.6288) -- (3.0173,4.6715) -- (3.0941,4.7142);
\draw[red,line width=0.45pt] (3.1124,1.5263) -- (3.0483,1.4908) -- (2.9843,1.4554) -- (2.9203,1.4199) -- (2.8563,1.3845) -- (2.7777,1.3412) -- (2.6991,1.2978) -- (2.6205,1.2545) -- (2.5563,1.2194) -- (2.4921,1.1843) -- (2.4279,1.1491) -- (2.3637,1.1140) -- (2.2849,1.0712) -- (2.2060,1.0283) -- (2.1272,0.9855) -- (2.0516,0.9448) -- (1.9760,0.9042) -- (1.9004,0.8635) -- (1.8247,0.8231) -- (1.7490,0.7827) -- (1.6733,0.7424) -- (1.6112,0.7096) -- (1.5491,0.6769) -- (1.4870,0.6441) -- (1.4249,0.6114) -- (1.3626,0.5790) -- (1.3003,0.5465) -- (1.2381,0.5141) -- (1.1758,0.4817) -- (1.1134,0.4496) -- (1.0510,0.4175) -- (0.9885,0.3854) -- (0.9261,0.3533) -- (0.8461,0.3127) -- (0.7661,0.2721) -- (0.6862,0.2316) -- (0.6260,0.2014) -- (0.5659,0.1713) -- (0.5057,0.1412) -- (0.4456,0.1111) -- (0.3826,0.0800) -- (0.3197,0.0490) -- (0.2567,0.0179);
\draw[red,line width=0.45pt] (0.1938,6.2700) -- (0.1333,6.2405) -- (0.0729,6.2111) -- (0.0124,6.1816);
\draw[red,line width=0.45pt] (0.0481,0.1310) -- (0.1114,0.1614) -- (0.1746,0.1918) -- (0.2379,0.2222) -- (0.3012,0.2526);
\draw[red,line width=0.45pt] (0.3012,0.2526) -- (0.3699,0.2853) -- (0.4385,0.3180) -- (0.5073,0.3505) -- (0.5761,0.3829) -- (0.6450,0.4152) -- (0.7139,0.4474) -- (0.7828,0.4796) -- (0.8517,0.5119) -- (0.9261,0.5462) -- (1.0004,0.5806) -- (1.0748,0.6149) -- (1.1492,0.6493) -- (1.2264,0.6845) -- (1.3036,0.7197) -- (1.3808,0.7550) -- (1.4580,0.7902) -- (1.5273,0.8216) -- (1.5967,0.8529) -- (1.6660,0.8843) -- (1.7353,0.9157) -- (1.8101,0.9492) -- (1.8849,0.9828) -- (1.9597,1.0164) -- (2.0344,1.0499) -- (2.1093,1.0834) -- (2.1841,1.1168) -- (2.2589,1.1502) -- (2.3338,1.1837) -- (2.4076,1.2165) -- (2.4814,1.2494) -- (2.5552,1.2823) -- (2.6290,1.3152) -- (2.7028,1.3481) -- (2.7766,1.3810) -- (2.8504,1.4139) -- (2.9242,1.4468) -- (2.9980,1.4797) -- (3.0718,1.5125) -- (3.1395,1.5429);
\draw[red,line width=0.45pt] (3.0760,4.7100) -- (3.0084,4.6797) -- (2.9407,4.6494) -- (2.8730,4.6191) -- (2.8053,4.5887) -- (2.7342,4.5567) -- (2.6630,4.5246) -- (2.5919,4.4925) -- (2.5279,4.4635) -- (2.4640,4.4345) -- (2.4000,4.4055) -- (2.3361,4.3763) -- (2.2722,4.3471) -- (2.2083,4.3180) -- (2.1480,4.2903) -- (2.0878,4.2626) -- (2.0275,4.2349) -- (1.9567,4.2021) -- (1.8859,4.1693) -- (1.8151,4.1364) -- (1.7480,4.1050) -- (1.6809,4.0736) -- (1.6137,4.0422) -- (1.5467,4.0106) -- (1.4797,3.9790) -- (1.4127,3.9473) -- (1.3493,3.9171) -- (1.2860,3.8869) -- (1.2226,3.8566) -- (1.1559,3.8245) -- (1.0891,3.7923) -- (1.0224,3.7601) -- (0.9593,3.7294) -- (0.8961,3.6987) -- (0.8330,3.6679) -- (0.7701,3.6369) -- (0.7071,3.6059) -- (0.6441,3.5750) -- (0.5813,3.5437) -- (0.5184,3.5124) -- (0.4556,3.4812) -- (0.3929,3.4497) -- (0.3301,3.4181) -- (0.2674,3.3866) -- (0.2014,3.3531) -- (0.1353,3.3195) -- (0.0693,3.2859) -- (0.0068,3.2539) -- (0.0556,3.0614) -- (0.1181,3.0934) -- (0.1838,3.1275) -- (0.2496,3.1616) -- (0.3154,3.1958) -- (0.3810,3.2301) -- (0.4467,3.2645) -- (0.5123,3.2989) -- (0.5813,3.3354) -- (0.6502,3.3719) -- (0.7192,3.4084) -- (0.7880,3.4451) -- (0.8568,3.4818) -- (0.9257,3.5186) -- (0.9943,3.5556) -- (1.0630,3.5926) -- (1.1317,3.6296) -- (1.1900,3.6612) -- (1.2483,3.6928) -- (1.3066,3.7245) -- (1.3683,3.7581) -- (1.4299,3.7918) -- (1.4916,3.8254) -- (1.5532,3.8592) -- (1.6147,3.8930) -- (1.6763,3.9268) -- (1.7447,3.9645) -- (1.8130,4.0022) -- (1.8813,4.0399) -- (1.9551,4.0808) -- (2.0288,4.1217) -- (2.1025,4.1626) -- (2.1763,4.2035) -- (2.2500,4.2443) -- (2.3267,4.2871) -- (2.4035,4.3298) -- (2.4802,4.3725) -- (2.5569,4.4152) -- (2.6337,4.4579) -- (2.7104,4.5006) -- (2.7871,4.5433) -- (2.8639,4.5860) -- (2.9406,4.6288) -- (3.0173,4.6715) -- (3.0941,4.7142);
\draw[red,line width=0.45pt] (3.1124,1.5263) -- (3.0483,1.4908) -- (2.9843,1.4554) -- (2.9203,1.4199) -- (2.8563,1.3845) -- (2.7777,1.3412) -- (2.6991,1.2978) -- (2.6205,1.2545) -- (2.5563,1.2194) -- (2.4921,1.1843) -- (2.4279,1.1491) -- (2.3637,1.1140) -- (2.2849,1.0712) -- (2.2060,1.0283) -- (2.1272,0.9855) -- (2.0516,0.9448) -- (1.9760,0.9042) -- (1.9004,0.8635) -- (1.8247,0.8231) -- (1.7490,0.7827) -- (1.6733,0.7424) -- (1.6112,0.7096) -- (1.5491,0.6769) -- (1.4870,0.6441) -- (1.4249,0.6114) -- (1.3626,0.5790) -- (1.3003,0.5465) -- (1.2381,0.5141) -- (1.1758,0.4817) -- (1.1134,0.4496) -- (1.0510,0.4175) -- (0.9885,0.3854) -- (0.9261,0.3533) -- (0.8461,0.3127) -- (0.7661,0.2721) -- (0.6862,0.2316) -- (0.6260,0.2014) -- (0.5659,0.1713) -- (0.5057,0.1412) -- (0.4456,0.1111) -- (0.3826,0.0800) -- (0.3197,0.0490) -- (0.2567,0.0179);
\draw[red,line width=0.45pt] (0.1938,6.2700) -- (0.1333,6.2405) -- (0.0729,6.2111) -- (0.0124,6.1816);
\draw[red,line width=0.45pt] (0.0481,0.1310) -- (0.1114,0.1614) -- (0.1746,0.1918) -- (0.2379,0.2222) -- (0.3012,0.2526);
\fill[black] (1.6137,0.8606) circle (1.4pt);
\fill[black] (3.1007,1.5255) circle (1.4pt);
\fill[black] (3.1106,1.5299) circle (1.4pt);
\fill[black] (3.1016,4.7215) circle (1.4pt);
\fill[black] (3.1121,4.7262) circle (1.4pt);
\fill[black] (3.1121,4.7242) circle (1.4pt);
\fill[black] (3.1025,4.7189) circle (1.4pt);
\fill[black] (3.1099,1.5249) circle (1.4pt);
\fill[black] (3.0995,1.5192) circle (1.4pt);
\draw[black,thick] (0.0281,1.2716) circle (3.2pt);
\draw[black,thick] (3.0568,4.9813) circle (3.2pt);
\node[right] at (0.1081,1.2716) {\footnotesize $s_A$};
\node[left] at (2.9768,4.9813) {\footnotesize $s_B$};
\node[blue] at (1.57,-0.55) {\footnotesize blue $=\Rp_t(Q_{1/3}+Q_{1/5})$};
\node[red] at (1.57,7.0332) {\footnotesize red $=\Rnat(\Qh{-1/2})$};
\end{tikzpicture}
\caption{The two Lagrangians at $q=5$ on the fundamental domain $[0,\pi]\times[0,2\pi)$ of the
pillowcase, plotted from the computed curves themselves (the pillowcase counterpart of Smith's
Figure~31). Blue is the perturbed Conway sum $\Rp_t(Q_{1/3}+Q_{1/5})$, a single immersed
circle with forty self-intersections clustered along the seams. The small sinusoidal arcs hugging the
seams $\gamma\in\{0,\pi\}$ are the cut-and-paste connectors resolving the four seam fiber circles,
drawn at the perturbation amplitude $\varepsilon\approx0.05$--$0.07$; these arcs carry the
self-crossings on which the bounding cochain lives, and the V-shaped turnbacks at the border are
strands reflecting off the seams in the quotient. Red is the earring
figure-eight $\Rnat(\Qh{-1/2})$, the doubled line of direction $(2,1)$ closing through the corner
folds. Across the interior the blue strands run \emph{nearly parallel} to red (slopes $8/15$ vs
$1/2$), so each interior band is a red line riding a blue one --- this near-tangency (crossing angle
$\approx0.026$) is why the interior generator exists and why shallow-angle corner tests are needed in
the computation. Solid dots are the nine generators: one interior, and two clusters of four near
$\gamma=\pi$ that merge at this scale. The two circled self-intersections of blue are the support
$s_A,s_B$ of the $q=5$ bounding cochain of Computation~\ref{comp:cochains}(i), one on each seam,
exchanged by $(\gamma,\theta)\mapsto(\pi-\gamma,-\theta)$. Curves appear as several arcs because the
fundamental domain folds the double cover.}
\label{fig:pillow}
\end{figure}

\subsection{Validation gates and the naive ranks}\label{ss:gate}
The reconstruction is checked before it is used. At $q=5$, red and blue meet in nine points (one
interior, two clusters of four near $\gamma=\pi$), the winding-number search
(\S\ref{sec:combinatorial}) finds exactly two immersed bigons with distinct vertices, and
\[
   \rk\HF\big((\Rnat,0),(\Rp_t,0)\big)=9-2\cdot2=5,
\]
matching \cite[Thm.~5.9]{Smith} in every particular. For the other members Smith gives no numbers; the
gates are internal: generator and bigon counts are recomputed at two independent perturbations, and
only perturbation-stable ranks are reported. (Generator counts themselves are not invariants and do
vary --- e.g.\ $19$ vs $23$ at $q=11$, $25$ vs $27$ at $q=13$ --- but the homology ranks agree in every
tested case. One non-generic earring perturbation at $q=7$, which collapses the thirteen generators to
nine, was identified and excluded.) The measured naive ranks are those of Table~\ref{tab:family}:
$5,5,7,15,17$ for $q=3,5,7,11,13$, giving Computation~\ref{comp:law} against
Theorem~\ref{thm:inat}. The $q=3$ value is the Hedden--Herald--Kirk computation of $8_{19}$
\cite[\S11.6]{HHK2}, where the naive theory already equals $\Inat$ and the cochain is trivial.

\section{The combinatorial Floer package}\label{sec:combinatorial}

\subsection{Polygons by winding numbers}
For immersed curves in a surface, Floer differentials count immersed bigons, detected combinatorially
by winding functions \cite{dSRS}. Fix generators $x,y$. A candidate bigon from $x$ to $y$ is a loop
$\Gamma=\alpha\cdot\bar\beta$ with $\alpha\subset$ red from $x$ to $y$ and $\beta\subset$ blue from $y$
to $x$; lift to $T^2$ and let $w$ be the winding function. Then $\Gamma$ bounds an immersed bigon iff
(a) $[\Gamma]=0\in H_1(T^2)$; (b) $w\equiv0$ at the four pillowcase corners; (c) $w\ge0$ on every
complementary region; (d) the corners at $x,y$ are convex (single embedded sector of angle $<\pi$ with
winding jump $+1$). The differential is $\partial x=\sum_y(\#\{\text{bigons}\}\bmod2)y$ and
$\rk\HF=\#\{\text{generators}\}-2\rk\partial$ over $\F_2$. The same conditions, with a convex-corner
test at \emph{every} vertex, detect the higher immersed polygons below. Delicate numerical points
(long edges under mod-$2\pi$ arithmetic, shallow corners, adaptive sampling) are handled as recorded
in the source.

\subsection{Lift bookkeeping}\label{ss:lift}
A pillowcase polygon lifts to exactly two $\iota$-related $T^2$ polygons; fixing the lift $C_+$ of red
selects exactly one, so pillowcase counts equal $T^2$ counts with red arc on $C_+$, with no division.
A pillowcase self-intersection of blue has two $T^2$ preimages, and a polygon may close through
either; contributions are accumulated over both. One pitfall is flagged for reproducibility: some
generators fold under $T^2\to\pill$, so proximity in $\pill$ is not proximity on the cover; all
locality pruning must be done in blue-arc position on the cover. (In an intermediate version of this
work a pillowcase-metric pruning silently dropped a genuine quadrilateral; the corrected runs are what
is reported here.)

\subsection{The deformed differential and the Maurer--Cartan equation}\label{ss:deformed}
For $\bc=\sum_ic_is_i$ ($c_i\in\F_2$) on blue, the deformed differential counts immersed polygons with
two generator vertices and the remaining vertices at crossings in the support \cite[\S2.9]{CHKK},
\cite[\S5]{Smith}:
\begin{equation}\label{eq:defdiff}
   \partial_\bc(x)=\sum_y\Big(\#\mathcal B(x,y)+\sum_i c_i\,\#\mathcal T(x,s_i,y)
     +\!\!\sum_{i<j}c_ic_j\,\#\mathcal Q(x,s_i,s_j,y)+\cdots\Big)y\pmod2,
\end{equation}
with $\mathcal B,\mathcal T,\mathcal Q$ the bigons, triangles, quadrilaterals ($\mu^1,\mu^2,\mu^3$).
The Maurer--Cartan equation \eqref{eq:MC} is the analogous count with all vertices at self-crossings:
monogons $\mu^0$, self-bigons $\mu^1$, self-triangles $\mu^2$, etc. The polygon counter was validated
on Smith's unlink prototype (where a single triangle through the earring pinch is the known
mechanism).

\begin{proposition}[Unobstructedness]\label{prop:unobstructed}
The blue Lagrangians bound no teardrops: $\mu^0=0$, so \eqref{eq:MC} is a genuine equation.
\end{proposition}

\begin{proof}
A teardrop is a Maslov-index-one disk with one corner, placing $\mu^0$ in degree $2$ of
$\CF(\Rp,\Rp)$; but a transverse self-intersection of a curve in a surface contributes generators in
degrees $0$ and $1$ only \cite{AkahoJoyce}, so $\CF^2=0$. (The argument requires disks in the smooth
stratum, where a $\Z$-grading exists; computationally every self-intersection lies at distance
$\ge0.6$ from every corner. Direct monogon counts confirm $\mu^0=0$, and the counter detects a genuine
teardrop on a test curve.) This is the standard mechanism by which graded curves in surfaces are
unobstructed; we record it because it is what makes the deformed theory well posed.
\end{proof}

The higher self-products vary across the family and matter: at $q=5$ also $\mu^1=0$ and $\mu^2=0$
(all pairs and all $\binom{40}3$ window-pruned triples tested), so Maurer--Cartan is vacuous on small
support; at $q=7$ and $q=11$ the self-differential $\mu^1$ is nonzero (two self-bigons each), so
\eqref{eq:MC} genuinely constrains $\bc$, and the computed cochains below pass it.

\section{The three cochains}\label{sec:compute}

\subsection{$q=5$: unique cancellation through a quadrilateral}\label{ss:b5}
The naive differential has rank $2$ (two bigons, pairs $(x_1,y_0)$ and $(x_4,y_6)$); the target rank
is $1$. Over $\F_2$ a deformation reaches rank $1$ only by cancelling one bigon entry exactly
(the added polygon terms must land on it). No triangle through any of the forty crossings reaches
either bigon pair; the cancellation happens one order up. There is an immersed quadrilateral with
boundary vertices $x_4,y_6$ and interior vertices $s_A,s_B$ (window-stable, hence a genuine immersed
disk); neither crossing carries any other polygon, so for $\bc=s_A+s_B$,
$\partial_\bc=\partial_0+E_{x_4,y_6}$ has the single entry $(x_1,y_0)$ and
$\rk\HF=9-2=7=\rk\Inat$. A search over all supports by increasing size shows no single crossing and no
other pair achieves rank $1$ --- e.g.\ the geometrically nearest cancelling pair drags in three
triangles and lands at rank $3$ --- so $\bc=s_A+s_B$ is the unique minimal solution; by the vacuity of
Maurer--Cartan on small support it is a bounding cochain. This proves
Computation~\ref{comp:cochains}(i).

\subsection{$q=7$: unique cancellation through a triangle}\label{ss:b7}
Thirteen generators, three bigons, naive rank $7$; target $9=\rk\Inat$ means rank $\partial_\bc=2$:
again a cancellation. Here a triangle suffices: a single self-crossing $s\approx(0.05,5.41)$ carries
an immersed triangle whose generator pair coincides with one bigon of $\partial_0$; $s$ carries no
other generator-touching polygon and is $\mu^1$-closed (it is the tail of no self-bigon), so $\bc=s$
satisfies \eqref{eq:MC} and cancels that bigon: $\rk\HF=13-4=9$. The search over all single crossings,
filtered by the Maurer--Cartan check, returns exactly this one; it is the unique minimal solution, and
it recurs at the same pillowcase coordinate under change of perturbation. This proves
Computation~\ref{comp:cochains}(ii). The contrast with $q=5$ --- triangle where a quadrilateral was
forced --- shows the polygon order of the correction is not a family invariant even within the deficit
regime.

\subsection{$q=11$: abundant creation}\label{ss:b11}
At the reported perturbation the complex has nineteen generators and naive rank
$15>13=\rk\Inat$: the correction must \emph{create} one differential, i.e.\ raise
$\rk\partial_\bc$ from $2$ to $3$. Creation is combinatorially generic: any immersed triangle through
a single crossing whose generator pair is \emph{not} already a differential adds a new entry.
Enumerating all triangles through the $225$ crossings ($108$ of them carry triangles), evaluating
$\rk\partial_\bc$, and filtering by the Maurer--Cartan check ($\mu^0=0$ everywhere; $\mu^1\ne0$, so
$\mu^1$-closedness is a real constraint) yields \emph{fifty-five} single-crossing bounding cochains
with deformed rank $3$, i.e.\ $\rk\HF=19-6=13=\rk\Inat$. Notably, in fifty of the fifty-five the
created differential flows into the same distinguished generator. This proves
Computation~\ref{comp:cochains}(iii).

\begin{remark}[Rigidity asymmetry]
At deficit members the rank condition pins the cochain uniquely; at the excess member it manifestly
does not. This is forced by the geometry of \eqref{eq:defdiff}: a cancelling polygon must land on an
occupied entry (a strong incidence condition on its vertices), while a creating polygon may land on
any empty entry. Consequently, at excess members the bounding cochain of the \emph{tangle} --- the
object the CHKK conjecture actually attaches --- is not determined by rank-matching with $\Inat$; any
further pinning must come from the naturality/invariance data of the conjecture itself. We regard this
as a genuine, and previously invisible, feature of the correction theory.
\end{remark}

\section{Discussion}\label{sec:disc}

\subsection{The law and the threshold}
Computation~\ref{comp:law} says the naive pillowcase theory is never more than one differential from
the truth on this family, with the error direction governed by $\det\gtrless3$. Two reformulations
suggest where a proof might come from. First, $\det=|q-6|<3$ happens exactly when the double branched
cover $\Sig_2(K_q)$ is an integral homology sphere; the deficit regime is the homology-sphere regime.
Second, with $d=(\det-1)/2$ the number of binary-dihedral traceless characters, the law reads
$\mathrm{naive}-\Inat=2\,\sgn(d-1)$: one binary-dihedral character is exactly compensated; zero leaves
a deficit; two or more leave an excess. Since the binary-dihedral characters sit at the pillowcase
seams --- where the Conway-sum fiber circles are resolved --- a curve-level explanation seems within
reach of the combinatorial model, and we pose it as the main open problem: \emph{prove the deficiency
law for all odd $q$ coprime to $3$.} A proof would convert Table~\ref{tab:family} from data into the
first family-wide statement about the size of the bounding-cochain correction.

\subsection{Relation to prior examples}
The one previously exhibited bounding cochain --- CHKK's, on the earring tangle of $T(4,5)$
\cite[\S10]{CHKK} --- acts by creation (rank $9\to7$). Our deficit members show that Conway-sum
cochains can act by cancellation, our excess member shows they can also act by creation, and the
family shows both behaviors occur on the \emph{same} tangle type, separated by the determinant. The
mechanism is thus not tied to the earring versus Conway-sum dichotomy, as the two prior data points
might have suggested, but to the deficiency sign.

\subsection{Reproducibility}
All computations are pure Python (standard library), included with the source; each module is a
self-checking battery. The Alexander recursion is validated by the eleven-coefficient Lehmer match at
$q=7$; the curve reconstruction by Smith's $q=5$ numbers; the polygon counter by the unlink prototype
and synthetic teardrop/lens tests; the naive ranks and cochains by independent perturbations.
$\rk\Inat$ in Table~\ref{tab:family} is Theorem~\ref{thm:inat} and is independent of all of this.

\begin{thebibliography}{CHKK22}

\bibitem[AJ10]{AkahoJoyce} M.~Akaho, D.~Joyce, \emph{Immersed Lagrangian Floer theory}, J.\ Differential
Geom.\ \textbf{86} (2010), 381--500. arXiv:0803.0717.

\bibitem[CHKK22]{CHKK} G.~Cazassus, C.~Herald, P.~Kirk, A.~Kotelskiy, \emph{The correspondence induced on the
pillowcase by the earring tangle}, J.\ Topol.\ \textbf{15} (2022), 2472--2543. arXiv:2010.04320.

\bibitem[dSRS14]{dSRS} V.~de~Silva, J.~Robbin, D.~Salamon, \emph{Combinatorial Floer homology}, Mem.\ Amer.\
Math.\ Soc.\ \textbf{230} (2014), no.\ 1080.

\bibitem[HHK14]{HHK1} M.~Hedden, C.~Herald, P.~Kirk, \emph{The pillowcase and perturbations of traceless
representations of knot groups}, Geom.\ Topol.\ \textbf{18} (2014), 211--287. arXiv:1301.0164.

\bibitem[HHK18]{HHK2} M.~Hedden, C.~Herald, P.~Kirk, \emph{The pillowcase and traceless representations of
knot groups II: a Lagrangian--Floer theory in the pillowcase}, J.\ Symplectic Geom.\ \textbf{16}
(2018), 721--815. arXiv:1501.00028.

\bibitem[HK24]{HK} C.~Herald, P.~Kirk, \emph{An endomorphism on immersed curves in the pillowcase},
arXiv:2407.11247.

\bibitem[Hir01]{Hironaka} E.~Hironaka, \emph{The Lehmer polynomial and pretzel links}, Canad.\ Math.\ Bull.\
\textbf{44} (2001), 440--451.

\bibitem[KM11a]{KM1} P.~Kronheimer, T.~Mrowka, \emph{Knot homology groups from instantons}, J.\ Topol.\
\textbf{4} (2011), 835--918. arXiv:0806.1053.

\bibitem[KM11b]{KM2} P.~Kronheimer, T.~Mrowka, \emph{Khovanov homology is an unknot-detector}, Publ.\ Math.\
IH\'ES \textbf{113} (2011), 97--208. arXiv:1005.4346.

\bibitem[Lim10]{Lim} Y.~Lim, \emph{Instanton homology and the Alexander polynomial}, Proc.\ Amer.\ Math.\
Soc.\ \textbf{138} (2010), 3759--3768.

\bibitem[Lin92]{Lin} X.-S.~Lin, \emph{A knot invariant via representation spaces}, J.\ Differential Geom.\
\textbf{35} (1992), 337--357.

\bibitem[Man18]{Manion} A.~Manion, \emph{The Khovanov homology of 3-strand pretzels, revisited}, New York J.\
Math.\ \textbf{24} (2018), 1076--1100. arXiv:1303.3303.

\bibitem[Smi24]{Smith} K.~Smith, \emph{Perturbed traceless $\SU$ character varieties of tangle sums},
arXiv:2412.06066.

\bibitem[Wue26]{WuebbenI} B.~J.~Wuebben, \emph{Trace-free $\SU$ characters and $\Z/4$ instanton gradings for
two-bridge and $(3,n)$-torus knots}, companion paper (2026).

\end{thebibliography}

\bigskip
\noindent{\sc Bernd J. Wuebben, New York, NY,} \texttt{wuebben@gmail.com}

\end{document}
